---
title: "Weather Analysis"
output: html_notebook
---

Understanding the correlation between weather on JSE.


# Import the data 
The historical weather data for varies parts of SA have been downloaded, accompanied with the movement of the JSE all shares index over the same period.
```{r}
# set working directory 
setwd("~/Desktop/Quanta_CS/analysis")

# import weather data
jhb = read.csv("../data/weather/johannesburg.csv")
ct = read.csv("../data/weather/capetown.csv")
dur = read.csv("../data/weather/durban.csv")
pta = read.csv("../data/weather/pretoria.csv")
blm = read.csv("../data/weather/Bloemfontein.csv")

# JSE data
jse = read.csv('../data/jse/JALSH.csv')
```

### Clean Stock Data
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)

# clean data
jse$Price = as.numeric(gsub(",", "",jse$Price))
jse$Open = as.numeric(gsub(",", "",jse$Open))
jse$Low = as.numeric(gsub(",", "",jse$Low))
jse$High = as.numeric(gsub(",", "",jse$High))

# Volume 
jse$Vol. = gsub("M", "000000", jse$Vol.)
jse$Vol. = gsub("B", "000000000", jse$Vol.)
jse$Vol. = as.numeric(jse$Vol.)
jse$Vol.[which(jse$Vol. < 10)] = jse$Vol.[jse$Vol. < 10]*10000

# Date
jse$Date = as.Date(jse$Date, format="%b %d, %Y")

# Keep: date, price & vol
jse = jse %>% select('Date', "Price", "Vol.")


```


# Examine Results
```{r}

# View Cleanup
head(jse)

# standardized price
jse$z_price = (jse$Price - mean(jse$Price))/sd(jse$Price)


# plot 
jse_plot <- ggplot(jse, aes(x=Date, y=Price)) + geom_line(col='darkblue') + ggtitle("JSE All Shares Index")
jse_plot_z <- ggplot(jse, aes(x=Date, y=z_price)) + geom_line(col='maroon') + ggtitle("JSE All Shares Index Standardized")

jse_plot
jse_plot_z


```


### View Temperature Data 
```{r}
library(dplyr)
library(docstring)

# Clean Date
jhb$Date = as.Date(jhb$date_time)
ct$Date = as.Date(ct$date_time)
dur$Date = as.Date(dur$date_time)
pta$Date = as.Date(pta$date_time)
blm$Date = as.Date(blm$date_time)





standard_mean_temp <- function(dataset) {
  " Return standardized temoerature - attached to dataframe " 
    daily_mean <- dataset %>% group_by(Date) %>% summarise(mean = mean(tempC)) 
    mean_z <- (daily_mean$mean - mean(daily_mean$mean))/sd(daily_mean$mean)
}


# compute std_z temperature 
jhb$temp_z = standard_mean_temp(jhb)
ct$temp_z = standard_mean_temp(ct)
dur$temp_z = standard_mean_temp(dur)
blm$temp_z = standard_mean_temp(blm)
pta$temp_z = standard_mean_temp(pta)



# create 1 dateset with temperatures
dataset = cbind(jhb$Date, jhb$temp_z,ct$temp_z, dur$temp_z, blm$temp_z, pta$temp_z)
colnames(dataset) = c("Date", 'jhb', 'ct', 'dur', 'blm', 'pta')
dataset = data.frame(dataset)

library(ggplot2)
ggplot(dataset, aes(x=Date, y=jhb)) + geom_line(col='red',alpha=0.3) +
  geom_line(aes(x=Date, y=ct), col='blue', alpha=0.3) + 
  geom_line(aes(x=Date, y=dur), col='darkgreen', alpha=0.3) + 
  geom_line(aes(x=Date, y=blm), col='black', alpha=0.3) + 
  geom_line(aes(x=Date, y=pta), col='lightblue', alpha=0.3) +
  ggtitle("Regular Temperature")


# correlation in temperature
dataset.corr = cor(dataset[,2:ncol(dataset)])

# plot correlation
library(corrplot)
corrplot(dataset.corr)

```







```{}

```
















# select desired columns
  t = t %>% select('Date', 'temp_z', 'z_price','Vol.') 
  
  
  print(paste("Correlation", cor(t$z_price, t$temp_z))) 





# visualize
ggplot(t, aes(x=Date, y=z_price)) + geom_line(col='darkgreen') +
  geom_line(aes(x=Date, y=temp_z), col='darkred') + ggtitle("Temp vs JSE")








